|

### 2021-12-02 appendix/appendix.Rmd
revisions - article intro, appendix, R script

1.  **Study sample**: Counties, Municipalities, States, Provinces, Countries.
2.  **Electoral systems**: Majoritarian, PR, Mixed.
3.  **Modelling strategies**: Panel data, Standard OLS, IV, RDD.
4.  **Institutional design**: Unicameral, Bicameral, or the Mixed of both Unicameral and Bicameral.

@@

f8 <- build_forest_het(aux, aux$coef,
                       aux$VAR, slab = aux$authoryear,
                       capt = NULL, lsize = 15,
                       ttl = 'Lower Chamber Size and Expenditure per Capita\n(subgrouping by the estimation technique)',
                       hetvar = aux$method)
```

@@

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Estimation Methods", warning=FALSE, cache=TRUE, echo = FALSE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita (RDD Only)", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

@@

f9 <- build_forest(mod, capt = NULL,
                       lsize = 15, ttl = 'Lower Chamber Size and Log Expenditure per Capita\n(subgrouping by RDD)')
```

@@

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
5. One notable absence in the analysis is the seminar paper by @petterssonlidbom2012size. The reason is because in that paper, the author uses Log of Expenditure Per Capita x Log of Legislature Size.

>>>>

1.  **Study sample**: Counties, Municipalities, States, Provinces, Countries.
2.  **Electoral systems**: Majoritarian, PR, Mixed.
3.  **Modelling strategies**: Panel data, Standard OLS, IV, RDD.
4.  **Institutional design**: Unicameral, Bicameral, or a Mix of both Unicameral and Bicameral.

@@

f8 <- build_forest_het(aux, aux$coef,
                       aux$VAR, slab = aux$authoryear,
                       capt = NULL, lsize = 15,
                       ttl = 'Lower Chamber Size and Expenditure per Capita\n(Subgrouping by Estimation Technique)',
                       hetvar = aux$method)
```

@@

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Estimation Method", warning=FALSE, cache=TRUE, echo = FALSE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

@@

```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita (RDDs)", warning=FALSE, cache=TRUE, echo = FALSE}
build_forest(mod, NULL)
```

@@

f9 <- build_forest(mod, capt = NULL,
                       lsize = 15, ttl = 'Lower Chamber Size and Log Expenditure per Capita\n(RDDs)')
```

@@

1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
3.  The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`. Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
5. One notable absence in the analysis is the seminar paper by @petterssonlidbom2012size. This is because the author uses Log of Expenditure Per Capita x Log of Legislature Size.

### 2021-12-02 article/article.Rmd
revisions - article intro, appendix, R script

We run meta-regressions to further evaluate the relationship between
legislature size and government expenditures. In those analyses, we measure the
effect of five moderators that capture different sources of heterogeneity in
the literature. In our Supplementary Materials, we also include binomial
tests to assess whether the proportions of positive and negative coefficients
are statistically different from each other, as well as funnel plots to test
for publication bias in existing research on the "law of $1/n$"
[@easterbrook1991publication; @gerber2001testing].

Aggregate results indicate that legislature size has no significant impact on
public spending. All of our main meta-analysis estimates show that the overall
effect is not statistically different from zero, thus confirming the
conflicting findings reported by the literature. However, when we look only at
articles that employ regression discontinuity designs (RDDs), we see that all
four papers included in our sample suggest that a higher number of legislators
leads to lower public spending [@debenedetto2018effect; @hohmann2017effect;
@lewis2019legislature; @petterssonlidbom2012size]. In this regard, it is
possible that methodological choices partially explain the divergent results
observed in the literature, as articles that use RDDs consistently point to the
same direction. One limitation of this finding is that these studies only test
the impact of lower house size and its natural logarithm on the natural
logarithm of expenditure per capita, thus it remains unclear whether the
results hold with other variables.

The meta-regressions provide additional evidence that our study sample is
highly heterogeneous and that effect sizes differ substantially according to
study specifications. When using an extended sample of `r dim(fulldat)[1]`
coefficients, we find that unicameralism is associated with higher public
spending, as predicted by the "law of $1/n$". Moreover, one of our
meta-regressions indicates that larger upper chambers spend more in terms of
per capita expenditure than lower chambers, a result that also appears in the
binomial tests. Overall, non-majoritarian voting systems seem to decrease
government spending, following the idea that the $1/n$ effect grows weaker as
the empirical cases distance from the original definition of the law. Finally,
meta-regression results confirm that regression discontinuity designs reduce
public spending estimates.

@@

\scriptsize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1.1cm}}
\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year, depvar2)
aux2 <- aux %>%
  mutate(depvar2 = 'aux') %>%
  unique()
for(i in 1:dim(aux)[1]) {
  if(aux2$depvar2[aux2$authoryear == aux$authoryear[i]] == 'aux') {
    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = aux$depvar2[i]
  } else {
    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = paste(
      aux2$depvar2[aux2$authoryear == aux$authoryear[i]],
      aux$depvar2[i], sep = ', ')
  }
}
aux <- aux2
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\scriptsize
\footnotetext{\scriptsize \textbf{Journal:} Unpub $=$ Unpublished, JPE $=$ Journal of Political
Economy, EJPE $=$ European Journal of Political Economy, PC $=$ Public Choice,
JPubE $=$ Journal of Public Economics, JPriE $=$ Journal of Private Enterprise,
APSR $=$ American Political Science Review, SEJ $=$ Southern Economic Journal,
UAR $=$ Urban Affairs Review, SCID $=$ Studies in Comparative International
Development, SSQ $=$ Social Science Quarterly, SPPQ $=$ State Politics and Policy
Quarterly, CPS $=$ Comparative Political Studies, RivPE $=$ Rivista di Politica
Economica, E\&P $=$ Economics and Politics, NTJ $=$ National Tax Journal.}
\footnotetext{\scriptsize \textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
international standard.} 
\footnotetext{\scriptsize \textbf{Dependent Variable:} ExpPC $=$ Per capita expenditure,
logExpPC $=$ Natural logarithm of per capita expenditure, PCTGDP $=$ Expenditure as
a percentage of GDP.}
\footnotetext{\scriptsize \textbf{Method:} OLS $=$ Ordinary least squares, IV $=$ Instrumental
variables, Panel $=$ Panel data/fixed effects, RDD $=$ Regression discontinuity
design.}
\footnotetext{\scriptsize \textbf{Electoral System:} M $=$ Majoritarian, NM $=$ Non-majoritarian (mixed or proportional
representation).} 
\end{minipage} 
\end{longtable}
\normalsize

@@

Our second procedure consists of employing multilevel random effect models
[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
extra levels to the regular meta-analysis, one including a unique publication
ID for each paper, and another building a common index for papers that share
the same data specifications. By adding these two levels, we account for
within- and between-study variation, thus removing these sources of effect size
dependency and improving the accuracy of the results. More information about
the multilevel models can be found in Section H.1 of the Supplementary
Material.

@@

We begin with the meta-analysis. We matched the house size variables with
our measures of government spending and created a theoretical $3 \times 3$
matrix. Out of the nine variable combinations, we found only seven the article
pool. Our sample does not contain any papers that analyse the relationships
between log lower chamber size and public expenditure per capita, or between
upper chamber size and the logarithm of public expenditure per capita.

@@

\begin{landscape}
\begin{figure}[!ht]
\centering
\caption{Forest plots of the relationship between legislature size and government spending (main sample)}
\vspace{0.3cm}
\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
\label{fig:plots}
\end{figure}
\end{landscape}

@@

\begin{figure}[htb]
\begin{center}
\caption{Forest plots of the relationship between legislature size and government spending with regression method heterogeneity (main sample)}
\vspace{.3cm}
\includegraphics[width=1\linewidth, height=7.8cm]{../graphs/graph2.pdf}
\label{fig:plots2}
\end{center}
\end{figure}

@@

\caption{Meta-regression results\label{tab:regressions}}

@@

Three estimates are statistically significant in the third set of
meta-regressions, which include public expenditure as a percentage of GDP as
the dependent variable. Both in our restricted and in our extended samples,
recent studies have smaller coefficients than older papers, which stands in
contrast with the first model. Institutional design also affects outcomes.
Papers that include mixed political systems report significantly lower
coefficients than those that analyse bicameral exclusively. Non-majoritarian
electoral systems have a small, positive effect in our extended sample model,
yet the coefficient is only significant at the 10\% level.

@@

In this letter, we use meta-analytic methods to assess the generality of the
"law of $1/n$". Based on a sample of `r length(unique(dat$id))` publications,
our meta-analyses show that there is no strong evidence that an increase in the
number of legislators has a significant effect on public expenditures. The
meta-regressions indicate that study characteristics have a considerable
influence on reported results. Electoral system affects the relationship
between legislature size and public expenditure, but the results are not
replicable in all estimations. In our extended sample, we find that
unicameralism favours the $1/n$ effect. Publication year generates conflicting
findings in our models, but recent papers tend to present smaller coefficients
than older ones. The meta-regressions confirm that modern estimation methods
such as RDDs and panel/fixed-effects models decrease effects more frequently
than OLS regressions. In a nutshell, we only find moderate support for the "law
of $1/n$" in unicameral governments and in the upper house, mostly when authors
used OLS estimators.

@@

In this sense, the empirical cases in the literature may not always be the most
fortunate testing ground for the "law of $1/n$". While we believe that moving
beyond the majoritarian districts framework could produce valuable insights,
institutional features that are central to the theory cannot be overrun. For
example, proportional representation (PR) electoral systems allow candidates
whose constituents are spread across large territories to provide diffused
public goods and win elections. However, geographically-targeted service
provision is at the very core of the legislative behaviour that produces the
"law of $1/n$". Thus, scholars should consider the possible implications of
these micro-level dynamics when applying the "law of $1/n$" logic to different
settings.

Another plausible reason why there is no clear-cut evidence in favour or
against the "law of $1/n$" may be that there are few incentives for the pure
accumulation of knowledge in the social sciences, at least when compared to the
benefits scholars may accrue when they challenge or add features to existing
theories [@geddes2003paradigms]. This leads to a reduced number of replication
studies and research syntheses in the field, although we have seen some
positive changes in this respect, such as EGAP's _Metaketa
Initiative_\footnote{See
\url{https://egap.org/our-work/the-metaketa-initiative} for further
information.}. Here we show that continuously producing and consuming
meta-analyses is a viable path towards knowledge-building in our discipline.
Although aggregating observational -- instead of experimental -- data can be
especially challenging, we believe that research synthesis methods play an
essential role in advancing our understanding of complex political phenomena.

@@

\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

>>>>

Aggregate results indicate that legislature size has no significant impact on
public spending. Our main meta-analysis estimates show that the overall effect
is not statistically different from zero, thus confirming the conflicting
findings reported by the literature. However, methodological choices partially
explain these divergent results. When we look only at articles that use
regression discontinuity designs (RDDs), all four papers included in our sample
consistently report a negative relationship between a higher number of
legislators and public expenditures. Our meta-regressions provide further
evidence that study designs significantly influence the results. Using a sample
of `r dim(fulldat)[1]` coefficients, we find that articles that use causal
inference methods report lower effects than those that use OLS, and that
unicameralism is associated with higher government expenditures.

@@

\scriptsize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1.1cm}}
\caption{Papers Included in the Meta-Analysis, Ordered by Year of Appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endfirsthead
\caption{Papers Included in the Meta-Analysis, Ordered by Year of Appearance (\textit{Continued})}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead
```{r papers, echo = FALSE, results = 'asis', cache = T}
build_nams <- function(x) {
  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
  if(length(x_) == 1) return(x_)
  else {
    aux <- x_[1]
      for (i in 2:length(x_))
        if (i == length(x_)){
          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
        } else {
          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
        }
  }
  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
                   sep = ''))
}
aux <- dat %>%
  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
  unique() %>%
  arrange(year, depvar2)
aux2 <- aux %>%
  mutate(depvar2 = 'aux') %>%
  unique()
for(i in 1:dim(aux)[1]) {
  if(aux2$depvar2[aux2$authoryear == aux$authoryear[i]] == 'aux') {
    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = aux$depvar2[i]
  } else {
    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = paste(
      aux2$depvar2[aux2$authoryear == aux$authoryear[i]],
      aux$depvar2[i], sep = ', ')
  }
}
aux <- aux2
for (i in 1:dim(aux)[1]) {
  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
}
```
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\scriptsize
\footnotetext{\scriptsize \textbf{Journal:} Unpub $=$ Unpublished, JPE $=$ Journal of Political
Economy, EJPE $=$ European Journal of Political Economy, PC $=$ Public Choice,
JPubE $=$ Journal of Public Economics, JPriE $=$ Journal of Private Enterprise,
APSR $=$ American Political Science Review, SEJ $=$ Southern Economic Journal,
UAR $=$ Urban Affairs Review, SCID $=$ Studies in Comparative International
Development, SSQ $=$ Social Science Quarterly, SPPQ $=$ State Politics and Policy
Quarterly, CPS $=$ Comparative Political Studies, RivPE $=$ Rivista di Politica
Economica, E\&P $=$ Economics and Politics, NTJ $=$ National Tax Journal.}
\footnotetext{\scriptsize \textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
international standard.} 
\footnotetext{\scriptsize \textbf{Dependent Variable:} ExpPC $=$ Per capita expenditure,
logExpPC $=$ Natural logarithm of per capita expenditure, PCTGDP $=$ Expenditure as
a percentage of GDP.}
\footnotetext{\scriptsize \textbf{Method:} OLS $=$ Ordinary least squares, IV $=$ Instrumental
variables, Panel $=$ Panel data/fixed effects, RDD $=$ Regression discontinuity
design.}
\footnotetext{\scriptsize \textbf{Electoral System:} M $=$ Majoritarian, NM $=$ Non-majoritarian (mixed or proportional
representation).} 
\end{minipage} 
\end{longtable}
\normalsize

@@

Our second procedure consists of employing multilevel random effect models
[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
extra levels to the regular meta-analysis, the first including a unique
publication ID for each paper, and a second one containing a common index for
papers that share the same data specifications. By adding these two levels, we
account for within- and between-study variation, thus removing these sources of
effect size dependency and improving the accuracy of the results. More
information about the multilevel models can be found in Section H.1 of the
Supplementary Material.

@@

We begin with the meta-analysis. We matched the house size variables with our
measures of government spending and created a theoretical $3 \times 3$ matrix.
Out of the nine variable combinations, we found only seven in the article pool.
Our sample does not contain any papers that analyse the relationships between
log lower chamber size and public expenditure per capita, or between upper
chamber size and the logarithm of public expenditure per capita.

@@

\begin{landscape}
\begin{figure}[!ht]
\centering
\caption{Forest Plots of the Relationship between Legislature Size and Government Spending (Main Sample)}
\vspace{0.3cm}
\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
\label{fig:plots}
\end{figure}
\end{landscape}

@@

\begin{figure}[htb]
\begin{center}
\caption{Forest Plots of the Relationship between Legislature Size and Government Spending with Regression Method Heterogeneity (Main Sample)}
\vspace{.3cm}
\includegraphics[width=1\linewidth, height=7.8cm]{../graphs/graph2.pdf}
\label{fig:plots2}
\end{center}
\end{figure}

@@

\caption{Meta-Regression Results\label{tab:regressions}}

@@

Three estimates are statistically significant in the third set of
meta-regressions, which include public expenditure as a percentage of GDP as
the dependent variable. Both in our restricted and in our extended samples,
recent studies have smaller coefficients than older papers, which stands in
contrast with the first model. Institutional design also affects outcomes.
Papers that include both unicameral and bicameral political systems report
lower coefficients than those that analyse bicameral exclusively.
Non-majoritarian electoral systems have a small, positive effect in our
extended sample model, yet the coefficient is only significant at the 10\%
level.

@@

In this letter, we use meta-analytic methods to assess the generality of the
"law of $1/n$". Based on a sample of `r length(unique(dat$id))` publications,
our meta-analyses show that there is no strong evidence that more legislators
increase public expenditures. The meta-regressions indicate that methodological
considerations have a considerable influence on reported results. In our
extended sample, we find that modern inference methods, such as RDDs, IVs and
panel data yield lower coefficients than OLS estimators. The models also
indicate that unicameralism favours the $1/n$ effect. The remaining moderators
show no consistent effects.

@@

In this sense, the empirical cases in the literature may not always be the most
fortunate testing ground for the "law of $1/n$". While we believe that moving
beyond the majoritarian districts framework could produce valuable insights,
institutional features that are central to the theory cannot be disregarded.
For example, proportional representation (PR) electoral systems allow
candidates whose constituents are spread across large territories to provide
diffused public goods and win elections. However, geographically-targeted
service provision is at the very core of the legislative behaviour that
produces the "law of $1/n$". Thus, scholars should consider the possible
implications of these micro-level dynamics when applying the "law of $1/n$"
logic to different settings.

Another plausible reason why there is no clear-cut evidence in favour or
against the "law of $1/n$" may be that there are few incentives for the pure
accumulation of knowledge in the social sciences, at least when compared to the
benefits scholars may accrue when they challenge or add features to existing
theories [@geddes2003paradigms]. This leads to a reduced number of replication
studies and research syntheses in the field, although we have seen some
positive changes in this respect, such as EGAP's _Metaketa
Initiative_\footnote{See
\url{https://egap.org/our-work/the-metaketa-initiative} for further
information.}. Here we show that meta-analyses provide a viable path towards
knowledge-building in our discipline. Although aggregating observational --
instead of experimental -- data can be especially challenging, we believe that
research synthesis methods play an essential role in advancing our
understanding of complex political phenomena.

@@

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}
